---
title: "Simulation"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(warn=-1)
library(parallel)
library(MASS)
library(tidyverse)
library(stats4)
library(knitr)
library(kableExtra)
library(lfe)
library(aod)
library(sandwich)
library(ggthemes)
library(stats)
```

## Simulation Setup

```{r data_generator}
set.seed(42)

# This function takes in model specification and simulation parameters to return a function that can be used to simulate the data on the individual level
simulate_data_generator <- function(y_model, samplesize_per_trial, no_trials,  sd.m_star = 3,
                          sd.y_star = 3, cor.m_star.y_star = 0.95,
                          num_treatment_group = 3,
                          mu.tau = c(0.5,1,2.5),
                          mu.gamma = c(0,1.5,3),
                          violate_A2 = FALSE,
                          violate_A3 = FALSE,
                          violate_A4 = FALSE
){
  func <- function(){
      # individual error structure
    mu <- c(m_star=0, y_star=0, noise_beta_correlated = 0) # means for m_star and y_star
    
    sd <- c(sd.m_star, sd.y_star, 0.5) # standard deviations
    cormat <- rbind(c(1,cor.m_star.y_star, 0.8),c(cor.m_star.y_star,1, 0.8), c(0.8, 0.8, 1))
    # var-cov matrix
    covmat <- diag(sd) %*% cormat %*% diag(sd) 
    
    df <- mvrnorm(samplesize_per_trial*no_trials,mu,covmat)%>%
      as_tibble()
    
    # Set model parameters
    phi <- runif(no_trials,-2,2)
    theta <- runif(no_trials,-2,2)
    trial_tau <- runif(no_trials,-3, 3)
    trial_gamma <- rep(0,no_trials)
    tau_innovation <- rnorm(samplesize_per_trial*no_trials,0,0.5)
    gamma_innovation <- rnorm(samplesize_per_trial*no_trials,0,0.5)
    beta_innovation <- rnorm(samplesize_per_trial*no_trials,0,0.5)
    
    if (violate_A2){
      beta_innovation <- df$noise_beta_correlated
    }
    if (violate_A3){
      complement <- function(y, rho, x) {
        # Generate a new vector correlates with y
        if (missing(x)) x <- runif(length(y),-1, 1) # Optional: supply a default if `x` is not given
        y.perp <- residuals(lm(x ~ y))
        rho * sd(y.perp) * y + y.perp * sd(y) * sqrt(1 - rho^2)
      }
      trial_gamma <- complement(trial_tau, 0.8)
    }
    if (violate_A4){
      trial_tau <- rep(0,no_trials)
    }
    df <- 
      df %>% mutate(    trial_index=row_number()%%no_trials+1,
                        treatment_group=trial_index%%num_treatment_group+1,
                        Ti = rbernoulli(samplesize_per_trial*no_trials),
                        phi_s = phi[as.vector(trial_index)], 
                        phi_s = phi[as.vector(trial_index)], 
                        phi_s = phi[as.vector(trial_index)], 
                        tau_s = mu.tau[as.vector(treatment_group)]+ trial_tau[as.vector(trial_index)],
                        theta_s = theta[as.vector(trial_index)],
                        gamma_s = mu.gamma[as.vector(treatment_group)]+trial_gamma[as.vector(trial_index)],
                        noise_tau=tau_innovation,
                        noise_gamma=gamma_innovation,
                        noise_beta=beta_innovation,
                        Mi = phi_s + tau_s*Ti+ m_star + noise_tau*Ti,
                        Yi = y_model(theta_s, gamma_s, Ti, Mi, y_star, noise_gamma, noise_beta)
      )%>%
      mutate(treatment_group=factor(treatment_group),
             trial_index=factor(trial_index))
  
    return(df)
  }
  return(func)
}

# Generate meta data from individual level data
get_meta_data <- function(individual_data, highest_degree = 1){
  # This function run simple regressions to estimate ATE for one trial on individual level data .
    regress_one_trial <- function(data, highest_degree){
      result <- lm(Yi~1+Ti, data=data)%>%summary
      delta_y <- result$coefficients['TiTRUE',1]
      delta_y_ste <- result$coefficients['TiTRUE',2]
      
      coeff_res = c('delta_y' = delta_y, 'delta_y_ste' = delta_y_ste)
      for (i in 1: highest_degree) {
          result <- lm(I(Mi^i)~1+Ti, data=data)%>%summary
          temp_delta <- result$coefficients['TiTRUE',1]
          names(temp_delta) = paste('delta_m', i, sep='')
          temp_delta_ste <- result$coefficients['TiTRUE',2]
          names(temp_delta_ste) = paste('delta_m', i, '_ste', sep='')
          coeff_res = c(coeff_res, temp_delta, temp_delta_ste)
      }
    out <- bind_rows(coeff_res)
    return(out)
  }
  meta_data <- individual_data%>%
      group_by(trial_index,treatment_group)%>%
      do(regress_one_trial(., highest_degree=highest_degree))%>%
      ungroup
  return(meta_data)
} 
```

## Potential Outcome Model

### Linear model
$Y_i =  (\beta+\epsilon_{i}^{\beta})\times M_i + (\gamma_s+ \epsilon_{i}^{\gamma}) \times T_i +  \theta_s + Y_i^*$ 

```{r model_1}
simu_model_1 <- function(theta_s, gamma_s, Ti, Mi, y_star, noise_gamma, noise_beta){
  beta <- 4
  Yi =  beta*Mi + theta_s + gamma_s*Ti + y_star + noise_gamma*Ti + noise_beta*Mi
  return(Yi)
}
```

#### We drew figure 3 under this model
```{r draw_graph}
# Draw graph
## Simple case, single treatment group
sim_data_func <- simulate_data_generator(simu_model_1, 400,20, 
                          sd.y_star = 6,
                          num_treatment_group = 1,
                          mu.gamma = c(3))
sim_data <- sim_data_func()
true_dose <- function(m) 4*m
samp_df <- sim_data%>%sample_n(100)

draw_df <- bind_rows(samp_df%>%
                       mutate(id= row_number())%>%
                       mutate(Mi=range(samp_df%>%dplyr::select(Mi))[1],
                              Yi = simu_model_1(theta_s, gamma_s, Ti, Mi, y_star, noise_gamma, noise_beta)),
                     samp_df%>%
                       mutate(id= row_number())%>%
                       mutate(Mi=range(samp_df%>%dplyr::select(Mi))[2],
                              Yi = simu_model_1(theta_s, gamma_s, Ti, Mi, y_star, noise_gamma, noise_beta)))

fit <- lm(Yi ~ 1+ Mi + Ti, data=samp_df)
scale = 0.3
g <- ggplot(data = samp_df, aes(x=Mi, y=Yi)) +
  geom_smooth(data =draw_df, 
              aes(x=Mi, y=Yi,group=id), 
              method='lm',se = F,
              color='grey',
              alpha = 0.5,
              size =1.2* scale)+
  geom_point(size =1.8 * scale)+
  # geom_smooth(method='lm',formula = str(fit$call), se = F, color = 'black', size =0.2)+
  geom_smooth(method='loess', se = F, color = 'black', size =1.8* scale)+
  stat_function(fun=true_dose, color='blue', size=2*scale)+
  labs(x='M',y='Y')+
  theme_few()
g
# ggsave('potential_outcomes.png',g,scale=scale)
```


#### A simple analysis with various methods on one simulation under this model
```{r simple_estimation}
# Heterogeneous direct treatment effects
sim_data <- simulate_data_generator(simu_model_1,1000,10)
sim_data_temp <- sim_data()
sim_data_temp <- sim_data_temp%>%bind_cols(
  as_tibble(model.matrix(~0+treatment_group,data = sim_data_temp)*sim_data_temp$Ti)%>%
    rename_at(vars(matches("treatment_group")),list(~paste(.,"Ti",sep =""))))

#  OLS SI (LSEM)
felm(Yi~1+Mi|factor(Ti):trial_index +trial_index|0|trial_index,data=sim_data_temp) %>% summary

# IV (sobel)
felm(Yi~1+Ti|trial_index|(Mi~trial_index:factor(Ti))|trial_index,data=sim_data_temp)%>%summary    
# IV equivalent
iv_form <- as.formula(paste("Yi~1+", 
                            paste(grep("treatment_group.*Ti", names(sim_data_temp), value=TRUE), 
                                  collapse = " + "),
                            "|trial_index|(Mi~trial_index:factor(Ti))|trial_index") )
felm(iv_form,data=sim_data_temp)%>%summary 

# Liml
felm(iv_form,data=sim_data_temp, kclass='liml')%>%summary    

# CMMA
meta_data <- get_meta_data(sim_data_temp, 1)
lm(delta_y ~ 1  + treatment_group + delta_m1, data=meta_data)%>%summary

```

### Quadratic Model
$Y_i =  (\beta_1+\epsilon_{i}^{\beta})\times M_i  +\beta_2*Mi^2 + (\gamma_s+ \epsilon_{i}^{\gamma}) \times T_i +  \theta_s + Y_i^*$ 

```{r model_2}
# Second model second degree polynomial
# Y_i = beta[1]*Mi + beta[2]*Mi^2 + theta_s + gamma_s*Ti + y_star

simu_model_2 <- function(theta_s, gamma_s, Ti, Mi, y_star, noise_gamma, noise_beta){
  beta <- c(4, 2)
  Yi =  beta[1]*Mi + beta[2]*Mi^2 + theta_s + gamma_s*Ti + y_star + noise_gamma*Ti + noise_beta*Mi
  return(Yi)
}
```

### Cubic Model
$Y_i =  (\beta_1+\epsilon_{i}^{\beta})\times M_i  +\beta_2*Mi^2 + \beta_3*Mi^3+ (\gamma_s+ \epsilon_{i}^{\gamma}) \times T_i +  \theta_s + Y_i^*$ 

```{r model_3}
# Third model third degree polynomial
# Y_i = beta[1]*Mi + beta[2]*Mi^2 + beta[3]*Mi^3  + theta_s + gamma_s*Ti + y_star 
simu_model_3 <- function(theta_s, gamma_s, Ti, Mi, y_star, noise_gamma, noise_beta){
  beta <- c(4, 0, 5)
  Yi =  beta[1]*Mi + beta[2]*Mi^2 + beta[3]*Mi^3  + theta_s + gamma_s*Ti + y_star + noise_gamma*Ti
  return(Yi)
}
```


## Estimation Function and Helper Functions
```{r estimation_func}
# Estimation results from single simulation
MC_single_sim<- function(index,simulate_data_f,CMMA_estimator_only=FALSE, DRF_degree=1, wald_test=FALSE){
    # if(index %%10==0){
    #   print(paste("Prcessing simulation no.",index))
    # }
    
    # get the simulated data
    sim_data <- simulate_data_f()
    # construct interaction terms between treatment groups and Ti
    sim_data <- sim_data%>%bind_cols(
      as_tibble(model.matrix(~0+treatment_group,data = sim_data)*sim_data$Ti)%>%
        rename_at(vars(matches("treatment_group")),list(~paste(.,"Ti",sep =""))))
    
    # prepare output data
    out <- data.frame(matrix(ncol = 3, nrow = 0))
    colnames(out) <- c("valname", "value", "model")
    out <- as_tibble(out)
    
    log_results <- function(out, m_vars, regres_summary, model_desc, IV=FALSE){
      for (i in seq_along(m_vars)){
        var <- m_vars[i]
        if (IV){
          var <- paste('`',var,'(fit)','`',sep='')
        }
        # Point estimates 
        point_est <- regres_summary$coefficients[, 1]
        # Standard Error
        std_est <- regres_summary$coefficients[, 2]
        if (length(point_est)==1 & length(m_vars)==1){
          names(point_est) = var
          names(std_est) = var
        }
        out <- out %>% 
          add_row(valname = paste('M',i,'_coef',sep = ''), 
                  value=point_est[var], 
                  model = model_desc)%>%
          add_row(valname = paste('M',i,'_std',sep = ''), 
                  value=std_est[var], 
                  model = model_desc)
      }
      return(out)
    }
      
    if (!wald_test){
    # get meta data
    meta_data <- get_meta_data(sim_data, DRF_degree)
    
    m_vars<-paste('delta_m',seq(1:DRF_degree), sep='')
    ## Proposed method (CMMA)
    regres <- lm(formula(paste('delta_y ~ 1 +treatment_group + ', 
                               paste(m_vars, collapse = '+'))), 
                 data=meta_data)%>%summary

    out <-  out%>%log_results(m_vars, regres, 'CMMA')

      if (CMMA_estimator_only == FALSE) {
        M_vars <- paste('I(Mi^',seq(1:DRF_degree),')', sep='')
        ## Simple pooled OLS (OLS SI)
        regres <- felm(formula(paste('Yi~1+', 
                             paste(M_vars, collapse = '+'),
                             '|factor(Ti):trial_index +trial_index|0|trial_index')),
                       data=sim_data)%>%summary
        out <-  out%>%log_results(M_vars, regres, 'pooled ols')

        ## IV method (small)
        regres <- felm(formula(paste('Yi~1+Ti|trial_index|(', 
                                     paste(M_vars, collapse ='|'), 
                                     '~trial_index:Ti)|trial_index')),
                       data=sim_data)%>%summary

        out <-  out%>%log_results(M_vars, regres, 'IV (small)', IV=T)

        ## proposed IV equivalent
        iv_form <- as.formula(paste("Yi~1+", 
                                    paste(grep("treatment_group.*Ti", names(sim_data), value=TRUE), 
                                          collapse = " + "),
                                    "|trial_index|(",
                                    paste(M_vars, collapse ='|'),
                                    "~trial_index:factor(Ti))|0") )
        
        regres <- felm(iv_form,data=sim_data)%>%summary    
        
        out <-  out%>%log_results(M_vars, regres, 'proposed IV equivalent', IV=T)

        ## Liml
        regres <- felm(iv_form,data=sim_data,kclass='liml')%>%summary    
        
        out <-  out%>%log_results(M_vars, regres, 'Liml equivalent')
      }

    }
    else
    {
      # get meta data
      meta_data <- get_meta_data(sim_data, 3)
      # This is code for wald test when hypothesized degree of DRF is 3
      m_vars<-paste('delta_m',seq(1:3), sep='')
      ## Proposed method (CMMA) with just M
      regres <- lm(formula(paste('delta_y ~ 1 +treatment_group + ', 
                                 paste(m_vars[1], collapse = '+'))), 
                   data=meta_data)%>%summary

      out <-  out%>%log_results(m_vars[1], regres, 'CMMA with M')

      ## Proposed method (CMMA) with just M and M^2
      regres <- lm(formula(paste('delta_y ~ 1 +treatment_group + ', 
                                 paste(m_vars[1:2], collapse = '+'))), 
                   data=meta_data)%>%summary

      out <-  out%>%log_results(m_vars[1:2], regres, 'CMMA with M, M^2')
      
      ## Proposed method (CMMA) with just M, M^2, and M^3
      regres_wald <- lm(formula(paste('delta_y ~ 1 +treatment_group + ', 
                                      paste(m_vars[1:3], collapse = '+'))), 
                        data=meta_data)
      regres <- regres_wald %>%summary

      out <-  out%>%log_results(m_vars[1:3], regres, 'CMMA with M, M^2 and M^3')

      # Wald Test
      # regress cubic
      wald <-  wald.test(b = coef(regres_wald), Sigma = vcov(regres_wald), Terms = 4)
      out <- out %>% 
        add_row(valname = "p value, m", value=wald$result$chi2['P'], model ='wald test')
      wald <-  wald.test(b = coef(regres_wald), Sigma = vcov(regres_wald), Terms = 5)
      out <- out %>% 
        add_row(valname = "p value, m2", value=wald$result$chi2['P'], model ='wald test')
      wald <-  wald.test(b = coef(regres_wald), Sigma = vcov(regres_wald), Terms = 6)
      out <- out %>% 
        add_row(valname = "p value, m3", value=wald$result$chi2['P'], model ='wald test')
      wald <- wald.test(b = coef(regres_wald), Sigma = vcov(regres_wald), Terms = 4:5)
      out <- out %>% 
        add_row(valname = "p value, m m2", value=wald$result$chi2['P'], model ='wald test')
      wald <- wald.test(b = coef(regres_wald), Sigma = vcov(regres_wald), Terms = c(4,6))
      out <- out %>% 
        add_row(valname = "p value, m m3", value=wald$result$chi2['P'], model ='wald test')
      wald <- wald.test(b = coef(regres_wald), Sigma = vcov(regres_wald), Terms = 5:6)
      out <- out %>% 
        add_row(valname = "p value, m2 m3", value=wald$result$chi2['P'], model ='wald test')
      wald <- wald.test(b = coef(regres_wald), Sigma = vcov(regres_wald), Terms = 4:6)
      out <- out %>% 
        add_row(valname = "p value, m m2 m3", value=wald$result$chi2['P'], model ='wald test')
    }
    out <- out%>%mutate(simulation_index=index)
    return(out)
}
```


```{r helper_funcs}
# This function runs the monte carlo simulation
mc_model_main <- function(y_model, samplesize_per_trial, no_trials, no_sims=100, CMMA_estimator_only=FALSE, DRF_degree=1, wald_test=FALSE,seed=42, ...){
  set.seed(seed)
  
  simulate_data_f = simulate_data_generator(y_model,samplesize_per_trial,
                                            no_trials, ...)
  # parameters for monte carlo 
  outcomes <- mclapply(1:no_sims, MC_single_sim, 
                       simulate_data_f=simulate_data_f,
                       CMMA_estimator_only=CMMA_estimator_only, 
                       DRF_degree=DRF_degree, 
                       wald_test=wald_test )
  outcomes <- outcomes %>% bind_rows%>%
    mutate("samplesize_per_trial"=samplesize_per_trial,"no_trials"=no_trials)
  return(outcomes)
}


# Compute coverage probabilities for the 90% and 95% CI and other stats from simulation results
stats_summary <- function(data,model_name,est_valname,std_valname, true_value,level=0.95){
  remove_outliers <- function(x, na.rm = TRUE, ...) {
    qnt <- quantile(x, probs=c(.25, .75), na.rm = na.rm, ...)
    H <- 5 * IQR(x, na.rm = na.rm)
    y <- x
    y[x < (qnt[1] - H)] <- NA
    y[x > (qnt[2] + H)] <- NA
    y
  }
  df <- data%>%filter(model==model_name)%>%
    spread(valname,value)%>%
    dplyr::select(est_valname,std_valname,samplesize_per_trial,no_trials)
  
  df <- df%>%rename(estimate=1, std=2)%>% 
    mutate_at(vars(estimate,std), remove_outliers)%>%
    mutate(CI.up = estimate + qnorm(0.5+level/2)*std,
           CI.lo = estimate - qnorm(0.5+level/2)*std,
           in_ci=CI.lo < true_value & true_value < CI.up)%>%
    summarise(ci_covprob = mean(in_ci,na.rm=T), 
              point.est = mean(estimate,na.rm=T),
              mse=mean((estimate-true_value)^2,na.rm=T),
              samplesize_per_trial=mean(samplesize_per_trial),
              no_trials=mean(no_trials),
              n= sum(!is.na(estimate)))%>%
    mutate(bias = point.est-true_value,
           rmse=sqrt(mse),
           Estimator=model_name)
  return(df)
}

simulation_summary <- function(data, models,est_valname,std_valname, true_value, level=0.95){
  lapply(models,
         stats_summary,
         data=data,
         est_valname=est_valname,
         std_valname=std_valname,
         true_value=true_value)%>%
  bind_rows()
}

get_avg_simulated_estimate <- function(data, model_name,est_valnames){
  data%>%filter(model==model_name)%>%
              filter(valname %in% est_valnames)%>%
              spread(valname,value)%>%
              dplyr::select(!!est_valnames)%>%
              summarise_all(mean)
}
# Get wald test result
wald_test_summary <- function(data, level=0.95){
  data%>%filter(model=='wald test')%>%
    spread(valname,value)%>%
    dplyr::select(-model,-samplesize_per_trial,-no_trials)%>%
    summarise_all(function(x) mean(x<(1-level)))
}
```

## Simulation Results

### Table 1: Finite-Sample Performance Comparison

```{r simulation, cache=TRUE}
# Table output
# ## Increase samplesize per trial
out <- lapply(c(200,500,1000), function(n) mc_model_main(simu_model_1, n, 50))

out%>%
  map(simulation_summary,
      models=c('CMMA','proposed IV equivalent','pooled ols','IV (small)', 'Liml equivalent'),
      est_valname='M1_coef',std_valname='M1_std', 4)%>%
  bind_rows()%>%
  mutate(ci_covprob = paste(round(ci_covprob*100,1),'%',sep = ''))%>%
  dplyr::select(samplesize_per_trial,no_trials,Estimator,bias,ci_covprob)%>%
  group_by(samplesize_per_trial)%>%
  group_split()%>%
  bind_cols()%>%
  dplyr::select(-matches('Estimator.'),
                -starts_with('no_trials'),
                -starts_with('samplesize_per_trial'))%>%
  mutate(Estimator = factor(Estimator, 
                            labels = c('LIML','CMMA','Full Sample 2SLS','Sobel(2008)' ,"LSEM {Baron1986}"),
                            levels=c('Liml equivalent','CMMA', 'proposed IV equivalent', 'IV (small)','pooled ols')))%>%
  arrange(Estimator)%>%
  kable(format="html",digits = 3,position = "center",align = "c",
        col.names = c("Estimator",
                                "Bias","95% CI coverage", 
                                "Bias","95% CI coverage", 
                                "Bias","95% CI coverage"),escape = F)%>%
  add_header_above(escape = F,c(" " = 1, "$N_{per}=200$" = 2,"$N_{per}=500$" = 2,"$N_{per}=1000$"=2))
```

### Table 2: Assumption Violation

```{r assumption_violation , cache=TRUE}
# Table output
# ## Assumption Violation

out3 <- lapply(c(200,500,1000), 
                   function(n) mc_model_main(simu_model_1,n,50, CMMA_estimator_only = T))%>%
  map(mutate,violation='None')
out3_A2 <-  lapply(c(200,500,1000), 
                   function(n) mc_model_main(simu_model_1,n,50, CMMA_estimator_only = T,  violate_A2 =T))%>%
  map(mutate,violation='A2')
out3_A3 <-  lapply(c(200,500,1000), 
                   function(n) mc_model_main(simu_model_1,n,50, CMMA_estimator_only = T,  violate_A3 =T))%>%
  map(mutate,violation='A3')
out3_A4 <-  lapply(c(200,500,1000), 
                   function(n) mc_model_main(simu_model_1,n,50, CMMA_estimator_only = T,  violate_A4 =T))%>%
  map(mutate,violation='A4')

lapply(list(out3, out3_A2, out3_A3, out3_A4), function(data){
  violation_str <- data[[1]]%>%select(violation)%>%pluck(1,1)
  data%>%map(simulation_summary,
             models=c('CMMA'),
             est_valname='M1_coef',std_valname='M1_std', 4)%>%
    bind_rows()%>%
    mutate(ci_covprob = paste(round(ci_covprob*100,1),'%',sep = ''),
           violation=!!violation_str)
}) %>% 
  bind_rows()%>%
  dplyr::select(samplesize_per_trial,no_trials,violation,bias,ci_covprob)%>%
  group_by(samplesize_per_trial)%>%
  group_split()%>%
  bind_cols()%>%
  dplyr::select(-matches('violation.'),
                -starts_with('no_trials'),
                -starts_with('samplesize_per_trial'))%>%
  mutate(violation = factor(violation,
                            levels=c('None','A2', 'A3', 'A4')))%>%
  arrange(violation)%>%
  kable(format="html",digits = 3,booktabs = T,position = "center",align = "c",
        col.names = c("Estimator",
                      "Bias","95% CI coverage", 
                      "Bias","95% CI coverage", 
                      "Bias","95% CI coverage"))%>%
  add_header_above(escape = F,c(" " = 1, "$N_{per}=200$" = 2,"$N_{per}=500$" = 2,"$N_{per}=1000$"=2))
```

### Table 3: Model Selection and Wald Tests
```{r wald_test , cache=TRUE}
# Wald test table
## mu(m) = beta2*m

out_model1 <-  mc_model_main(simu_model_1,1000,100, DRF_degree=3, wald_test= TRUE)
## mu(m) = beta2*m + beta3*m^2
out_model2 <-  mc_model_main(simu_model_2,1000,100, DRF_degree=3, wald_test= TRUE)
## mu(m) = beta2*m + 0 + beta4*m^3
out_model3 <-  mc_model_main(simu_model_3,1000,100, DRF_degree=3, wald_test= TRUE)

bind_rows(
  out_model1%>%
  wald_test_summary%>%
  dplyr::select(`p value, m3`,`p value, m2 m3`,`p value, m m2 m3`)%>%
  mutate(`$\\mu(m)$`='$4m$',
         degree = 1,
         estimate=out_model1 %>%
           get_avg_simulated_estimate('CMMA with M', c('M1_coef'))%>%
           as_vector()%>%round(3)%>%paste(collapse=', ')),
  out_model2%>%wald_test_summary%>%
  dplyr::select(`p value, m3`,`p value, m2 m3`,`p value, m m2 m3`)%>%
  mutate(`$\\mu(m)$`='$4m + 2m^2$',
         degree = 2,
         estimate=out_model2 %>%
           get_avg_simulated_estimate('CMMA with M, M^2',c('M1_coef','M2_coef'))%>%
           as_vector()%>%round(3)%>%paste(collapse=', ')),
  out_model3%>%wald_test_summary%>%
  dplyr::select(`p value, m3`,`p value, m2 m3`, `p value, m m2 m3`)%>%
  mutate(`$\\mu(m)$`='$4m + 0m^2 + 5m^3$',
         degree = 3,
         estimate=out_model3 %>%
           get_avg_simulated_estimate('CMMA with M, M^2 and M^3',c('M1_coef','M2_coef', 'M3_coef'))%>%
           as_vector()%>%round(3)%>%paste(collapse=', ')))%>%
  dplyr::select(`$\\mu(m)$`,everything())%>%
  kable(format="html",digits = 2,booktabs = T,escape=FALSE, position = "center",align = "c",
        col.names = c("$\\mu(m)$","$H_0: \\beta_3 = 0$","$H_0: \\beta_2 = \\beta_3 = 0$",
                      "$H_0: \\beta_1=\\beta_2=\\beta_3= 0$", "Highest degree used",
                      "Results"))%>%
  add_header_above(c(" "=1, "% of Wald Tests Rejecting $H_0$" = 3,"CMMA Estimation"=2))

```
